The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-19 RET_Hosts_IR.tex

\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
\label{fig:histfit}}
\end{figure*}

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
\label{fig:param_diffs}}
\end{figure*}

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
\label{fig:param_diffs}}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s12_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SESNe, accounting for uncertainties in each bin.
\label{fig:histfit_s12_ssfr}}
\end{figure*}

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
\label{fig:param_diffs}}
\end{figure*}

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
\caption{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs. Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig. \ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason.
\label{fig:corner}}
\end{figure*}
